### 2018-04-12 includes/stringfuzz.tex
Removing redundant text.

\noindent and each term is recursively defined as any one of: repetition
(\texttt{re.*}), Kleene star (\texttt{re.+}), union (\texttt{re.union}), or a
character literal. Nested operators are nested up to a specified depth of
recursion. Terms at depth 0 are always regex constants.

Intuitively, each instance is a concatenation of regex terms, where each
term is a random nested regex operator with random arguments
(up to a specified depth) terminating in a regex literal.
Below are three example regexes (in regex syntax, not in the SMT-LIB language)
of depth 2 that can be produced by this scheme:
\begin{align*}
    & ((\texttt{a}|\texttt{b})|(\texttt{cc})+)\quad\quad\quad
    ((\texttt{ddd})*)+\quad\quad\quad ((\texttt{ee})+|(\texttt{fff})*)
\end{align*}

>>>>

\noindent and each term \texttt{Ti} is recursively defined as any one of: repetition
(\texttt{re.*}), Kleene star (\texttt{re.+}), union (\texttt{re.union}), or a
character literal. Nested operators are nested up to a specified (using
the \texttt{--depth} flag) depth of recursion. Terms at depth 0 are
regex constants. Below are 3 example regexes (in regex, not SMT-LIB, syntax)
of depth 2 that can be produced this way:
\begin{align*}
    & ((\texttt{a}|\texttt{b})|(\texttt{cc})+)\quad\quad\quad
    ((\texttt{ddd})*)+\quad\quad\quad ((\texttt{ee})+|(\texttt{fff})*)
\end{align*}
